\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-27 paper/ms.tex
Add sed figure and other tweaks

\newcommand{\todo}[1]{{TODO: #1}}

@@

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search for comoving stars using the proper motions and parallaxes
from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(Table~\ref{tab:t1}).

@@

We estimate that the accretion of $\approx 15$~\mearth\ of rocky planets
in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
refractory elements as well as the surface Li abundance.
Because the anchor star, \sunanalog,
is very similar to the Sun in its stellar properties (\teff, \logg, \feh, age),
we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
pre-accretion state of \bizarreone.
In \figname~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth composition
material\cite{2003TrGeo...2..547M} assuming that 2\% of the star's mass is in
its convective zone\cite{Pinsonneault:2001aa}.
It has long been known that more volatile (low \Tcondens) elements are more
depleted in the Earth relative to CI or other carbonaceous
chondrites\cite{mcdonough2001composition} that are thought to reflect the
elemental composition of the proto-solar nebula. \todo{Check end of last sentence}
This trend is presumed to be closely related to the formation of terrestrial
planets and, in particular to the radial temperature gradient in a
protoplanetary disk.
The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
good match to the observed $\Delta\elemH{X}$, suggesting that the
refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
rocky planetary material than \sunanalog.

@@

\section{Acknowledgements}
We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
for their valuable feedback.
The Flatiron Institute is supported by the Simons Foundation.
% Gaia
This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
% software
%\software{
%  %The data and code used in this project is available from
%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
%  %software license.
%  This research utilized:
%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
%  \texttt{IPython} (\citealt{Perez:2007}),
%  \texttt{matplotlib} (\citealt{Hunter:2007}),
%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
%  and \texttt{pandas} (\citealt{pandas}).}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Comparison to other pairs that show abundance differences.
    %TODO
    Abundance differences of the \bizarreone-\sunanalog\ pair
    ranked by the condensation temperature of elements for solar composition gas
    from \citet{2003ApJ...591.1220L}.
    The condensation temperature may be read from the gray line and right y-axis.
    We show three wide binary systems selected from the literature:
    HD~20782/1 (\citet{Mack:2014aa}, $\feh\approx0$),
    XO-2N/S\cite{Biazzo:2015aa} ($\feh\approx0.35$)),
    and WASP-94AB\cite{Teske:2016aa} ($\feh\approx0.3$).
    Locations of elements with at least one measurement from any study
    are indicated by a vertical line and its symbol.
    Note that often multiple values are reported for one element corresponding
    to different ionization states in equivalent width analyses.
    No other pair studied so far were shown to have such large difference
    in metallicity or sharp contrast between (moderately) volatile and
    refractory elements as \bizarreone-\sunanalog.
  }
  \label{fig:relabun_tcrank}
\end{figure}

@@

Combining the precise radial velocities obtained from spectra with the \tgas\
astrometry, we can compare differences between the inferred 6D phase-space
coordinates of the two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, and proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
We assume the noise is Gaussian, and the radial velocity measurement is
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix, and $\mathcal{N}$ is
normal (Gaussian) distribution (see also appendices of
\citealt{2017AJ....153..257O}).
We adopt a uniform space-density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$:
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}\cite{2013PASP..125..306F}
to generate posterior samples in $(r, v_\alpha, v_\delta, v_r)$
by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the Heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
(-11.1,\,244,\,7.25)~\kms$\cite{Schonrich:2010, Schonrich:2012}.

@@

%TODO: plot styles...
\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
    Sun (grey).
    For \sunanalog, the initial conditions are set to the median of the
    posterior samples over the phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
    integration scheme implemented in \project{Gala} (\citealt{gala}).
    Right panel: distribution of maximum $z$-heights for orbits computed from
    all posterior samples.
  }
  \label{fig:orbit}
\end{figure}

The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning.
Thus, surface lithium abundance is an indicator of stellar ages.
The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
solar lithium abundance and rotational profile\cite{2005Sci...309.2189C}.
The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
among all measured elements.
This translates to a $\sim 500$~Myr difference in age.
Given the overall higher metal abundances and the peculiar abundance patterns
in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
abundance means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been
attributed to the engulfment of substellar companions such as gas giant planets
or brown dwarfs which may replenish $\elem{Li}$\cite{Casey:2016aa}.

In fact, the surface lithium abundance is the only indication that points to
younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving pairs
using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\todo{needs refernces}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
found no evidence for indications of activity or infrared excess in their
spectral energy distributions.
The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential (similar to \texttt{MWPotential2014} from
\cite{Bovy:2015}) using \project{Gala} (\cite{gala}).
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\todo{needs references for vertical action as age indicator}).
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that their unusually high \elem{Li} abundance
requires an alternative explanation; our favored explanation being the accretion
of rocky, Lithium-rich material.

@@

@@

Here we estimate how much added rocky material is needed to explain an
increment of $\approx 0.2$~dex in refractory elements observed in \bizarreone\
relative to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx XX$,
$\delta\logg \approx XX$, and $\Delta\feh \approx 0$),
we may approximate the pre-accretion abundances of \bizarreone\ as being
equivalent to the sun.
We carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding a certain mass of bulk Earth
composition under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}
We take the solar abundances\cite{Asplund:2009aa}, $\elemH{X}$, of element \elem{X}
which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in, e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element is $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth\cite{mcdonough2001composition}
as a proxy for rocky planet composition. We adopt $f_\mathrm{CZ} = 0.02$ for
the fraction of mass in the convective zone\cite{Pinsonneault:2001aa}.

>>>>

\newcommand{\todo}[1]{{\color{red}TODO: #1}}

@@

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search\cite{2017AJ....153..257O} for comoving stars using the
proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
catalog (hereafter \tgas), a component of the first data release of the
astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(Table~\ref{tab:t1}).

@@

We estimate that the accretion of $\approx 15$~\mearth\ of rocky planets
in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
refractory elements as well as the surface Li abundance.
Because the anchor star, \sunanalog,
is very similar to the Sun in its stellar properties (\teff, \logg, \feh, age),
we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
pre-accretion state of \bizarreone.
In \figname~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth composition
material\cite{2003TrGeo...2..547M} assuming that 2\% of the star's mass is in
its convective zone\cite{Pinsonneault:2001aa}.
It has long been known that more volatile (low \Tcondens) elements are more
depleted in the Earth relative to CI or other carbonaceous
chondrites\cite{mcdonough2001composition} that are thought to reflect the
elemental composition of the proto-solar nebula.
This trend is presumed to be closely related to the formation of terrestrial
planets and, in particular to the radial temperature gradient in a
protoplanetary disk.
The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
good match to the observed $\Delta\elemH{X}$, suggesting that the
refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
rocky planetary material than \sunanalog.

@@

\section{Acknowledgements}
We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
for their valuable feedback.
The Flatiron Institute is supported by the Simons Foundation.
% Gaia
This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
% 2MASS
This publication makes use of data products from the Two Micron All Sky Survey,
which is a joint project of the University of Massachusetts and the Infrared
Processing and Analysis Center/California Institute of Technology, funded by
the National Aeronautics and Space Administration and the National Science
Foundation.
% all-WISE
This publication makes use of data products from the Wide-field Infrared Survey
Explorer, which is a joint project of the University of California, Los
Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
funded by the National Aeronautics and Space Administration.
% software
%\software{
%  %The data and code used in this project is available from
%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
%  %software license.
%  This research utilized:
%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
%  \texttt{IPython} (\citealt{Perez:2007}),
%  \texttt{matplotlib} (\citealt{Hunter:2007}),
%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
%  and \texttt{pandas} (\citealt{pandas}).}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Comparison to other pairs that show abundance differences.
    %TODO
    Abundance differences of the \bizarreone-\sunanalog\ pair ranked by the
    condensation temperature of elements for solar composition
    gas\cite{2003ApJ...591.1220L}.
    The condensation temperature may be read from the gray line and right y-axis.
    We show three wide binary systems selected from the literature:
    HD~20782/1\cite{Mack:2014aa} ($\feh\approx0$),
    XO-2N/S\cite{Biazzo:2015aa} ($\feh\approx0.35$),
    and WASP-94AB\cite{Teske:2016aa} ($\feh\approx0.3$).
    Locations of elements with at least one measurement from any study
    are indicated by a vertical line and its symbol.
    Note that often multiple values are reported for one element corresponding
    to different ionization states in equivalent width analyses.
    No other pair studied so far were shown to have such large difference
    in metallicity or sharp contrast between (moderately) volatile and
    refractory elements as \bizarreone-\sunanalog.
  }
  \label{fig:relabun_tcrank}
\end{figure}

@@

Combining the precise radial velocities obtained from spectra with the \tgas\
astrometry, we can compare differences between the inferred 6D phase-space
coordinates of the two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, and proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
We assume the noise is Gaussian, and the radial velocity measurement is
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix, and $\mathcal{N}$ is
normal (Gaussian) distribution\cite{2017AJ....153..257O}.
We adopt a uniform space-density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$:
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}\cite{2013PASP..125..306F}
to generate posterior samples in $(r, v_\alpha, v_\delta, v_r)$
by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the Heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
(-11.1,\,244,\,7.25)~\kms$\cite{Schonrich:2010, Schonrich:2012}.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.65\linewidth]{sed.pdf}
  \end{center}
  \caption{Spectral energy distributions of \bizarreone\ and \sunanalog.
    We compiled the photometric measurements from
    \project{Tycho-2}\cite{2000A&A...355L..27H},
    \project{2MASS}\cite{2006AJ....131.1163S}, and
    \project{WISE}\cite{2010AJ....140.1868W}.
  }
  \label{fig:sed}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{Left panel: Galactic orbits computed for \sunanalog\ (blue) and the
    Sun (grey).
    For \sunanalog, the initial condition is set to the median of the
    posterior samples over the phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
    integration scheme implemented in \project{Gala}\cite{gala}.
    Right panel: Distribution of maximum $z$-heights for orbits computed from
    all posterior samples for \sunanalog.
  }
  \label{fig:orbit}
\end{figure}

We provide a more detailed discussion of stellar ages and coevality of
\bizarreone-\sunanalog\ pair, especially on whether the stars may be
very young ($\lesssim 1$~Gyr).
The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning.
Thus, surface lithium abundance can be an indicator of stellar ages.
The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\ implies an age
of $\lesssim 1$~Gyr according to the theoretical models tuned to explain the
solar lithium abundance and rotational profile\cite{2005Sci...309.2189C}.
The lithium abundance of \bizarreone\, $2.74$~dex, shows the largest difference
among all measured elements.
This translates to a $\sim 500$~Myr difference in age.
Given the overall higher metal abundances and the peculiar abundance patterns
in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
abundance means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been
attributed to the engulfment of substellar companions such as gas giant planets
or brown dwarfs which may replenish $\elem{Li}$\cite{Casey:2016aa}.

In fact, the surface lithium abundance is the only indication that points to
younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger comoving group of stars.
However, there is no evidence in our search\cite{2017AJ....153..257O} of
comoving pairs using \tgas\ that the two stars belong to a larger group of
young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\todo{needs refernces}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
found no evidence for indications of activity or infrared excess in their
spectral energy distributions (\figname~\ref{fig:sed}).
The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential\cite{Bovy:2015} using \project{Gala}\cite{gala}.
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\figname~\ref{fig:orbit}).
%TODO:APW needs references for vertical action as age indicator
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that their unusually high \elem{Li} abundance
requires an alternative explanation; our favored explanation being the accretion
of rocky material that has locked lithium.

@@

\subsubsection{Exchange Scattering}
\label{sub:exchange_scattering}

Although the data described above strongly suggests that the two stars are
coeval, we may still consider scenarios in which the two stars are not actually
born together.
Two stars unrelated at birth may end up in a binary system via a binary-single
scattering event that results in an exchange of binary members.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\cite{Hut:1983ab,Hut:1983aa}
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
  \label{eq:crosssection}
\end{eqnarray}
where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
\end{eqnarray}
\eqname~\ref{eq:crosssection} is appropriate when $v_i/v_c \gg 1$,
which is the case for wide binaries
scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars with a constant
number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
$10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk stars in
any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
\end{eqnarray}
which is low enough to be negligible.

In fact, any exchange scattering scenario is unsatisfactory as typical
field stars with similar metallicities as \bizarreone\ and \sunanalog\ is very
unlikely to show the abundance difference pattern observed.
In \figname~\ref{fig:deltaXH}, we compare the abundance difference of
\bizarreone-\sunanalog\ with the distribution of abundance differences,
$\Delta[\elem{X}/\elem{H}]$, between random pairings of two stars with similar
\feh\ as \bizarreone\ and \sunanalog.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are typically enhanced at a similar level, with some variations.
Specifically, for a typical star with $\feh \approx 0.2$~dex, we generally
expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
\cite{Battistini:2015aa,Bensby:2003aa}, making the low
[\elem{Na}/\elem{Fe}] and [\elem{Mn}/\elem{Fe}] seen in \bizarreone\ very
unlikely to arise from variations in Galactic chemical evolution.

@@

We estimate how much added rocky material is needed to explain an
increment of $\approx 0.2$~dex in refractory elements observed in \bizarreone\
relative to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx XX$,
$\delta\logg \approx XX$, and $\Delta\feh \approx 0$),
we may approximate the pre-accretion abundances of \bizarreone\ as being
equivalent to the sun.
We carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding a certain mass of bulk Earth
composition under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}
We take the solar abundances\cite{Asplund:2009aa}, $\elemH{X}$, of element \elem{X}
which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in, e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element is $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth\cite{mcdonough2001composition}
as a proxy for rocky planet composition. We adopt $f_\mathrm{CZ} = 0.02$ for
the fraction of mass in the convective zone\cite{Pinsonneault:2001aa}.
